---
title: "Valmyndigheten"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Valmyndigheten}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup,eval=TRUE}
library(Valmyndigheten)
```


**Description**

This package is used to get the data of preliminary election results, polling station vote count and assembly districts count from excel files present in Valmyndigheten XML.

**Installation** 

The Package can be downloaded from.
    
    devtools::install_github("akshath-aks/Valmyndigheten")

**Vignette**

After installation run the code below to find vignettes.
    
    browseVignettes('Valmyndigheten')
    
    
**Shiny-app**

To view visualization of the retrieved data, run the below code.

    runGitHub('shiny-app','akshath-aks')
    
**Attributes defined in the Class **    

    Linreg Class contains following attribute
        *Content: Parsed data
        *Path: Path of the data in excel file.
        *response: Response from the GET function.

**Parameter in the package **

path :specifies the path for excel file to be downloaded

**Methods**

1.Class : Valmyndigheten_api()

Retrieve Parsed data Contents of the Excel for the given path(url)

2.get_p()

Return cleaned data from excel file(get the data of polling station vote count)

3.get_p_a()

Return cleaned data from excel file(get the data of assembly districts count)

4.get_combined_data()

combined data from get_p() and get_p_a() functions(Combine the data of polling station count and assembly districts count)

**Examples**

    ```{r,include=TRUE,eval=TRUE,echo=TRUE}
    
    path<-'18.14c1f613181ed0043d567ae/1663009000443/valresultat-riksdagen-preliminar-jamforande-statistik.xlsx'
    
    ```

      
After calling the above function it returns

    ```{r,include=TRUE,eval=TRUE,echo=TRUE}
    
    Valmyndigheten_api(path)[[1]][1:2]
    
    ```
    

    ```{r,include=TRUE,eval=TRUE,echo=TRUE}
    
      get_p()[1:5,c(1,3)]
    
    
    ```
    
    
Another Path for get_p_a() function


    ```{r,include=TRUE,eval=TRUE,echo=TRUE}
    
    path_a<-'18.14c1f613181ed0043d56f51/1663745020932/preliminar-riksdagsval-jamforande-statistik-2018-2022-med-uppsamlingsdistrikt-ny.xlsx'
    
    ```

    ```{r,include=TRUE,eval=TRUE,echo=TRUE}
    
    Valmyndigheten_api(path_a)[[1]][1:2]
    
    ```


    ```{r,include=TRUE,eval=TRUE,echo=TRUE}
    
      get_p_a()[2,c(1,3)]
    
    
    ```
 

Getting combined data.
 
    ```{r,include=TRUE,eval=TRUE,echo=TRUE}
    
      get_combined_data()[1:5,c(1,3)]
    
    
    ```
    
          