---
title: "Valmyndigheten"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Valmyndigheten}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(Valmyndigheten)
```


**Description**

This package is used to get the data of preliminary election results, polling station vote count and assembly districts count from excel files present in Valmyndigheten XML.

**Installation** 

The Package can be downloaded from.
    
    devtools::install_github("akshath-aks/Valmyndigheten")

**Vignette**

After installation run the code below to find vignettes.
    
    browseVignettes('Valmyndigheten')
    
**Shiny-app**

To view visualization of the retrieved data, run the below code.

    runGitHub('shiny-app','akshath-aks')
    
**Attributes defined in the Class **    

    Linreg Class contains following attribute
        *Content: Parsed data
        *Path: Path of the data in excel file.
        *response: Response from the GET function.

**Parameter in the package **

path :specifies the path for excel file to be downloaded

**Methods**

1.Class : Valmyndigheten_api()

Retrieve Parsed data Contents of the Excel for the given path(url)

2.get_p()

Return cleaned data from excel file(get the data of polling station vote count)

3.get_p_a()

Return cleaned data from excel file(get the data of assembly districts count)

4.get_combined_data()

combined data from get_p() and get_p_a() functions(Combine the data of polling station count and assembly districts count)

**Examples**


    1)  path<-'18.14c1f613181ed0043d567ae/1663009000443/valresultat-riksdagen-preliminar-jamforande-statistik.xlsx'
        Valmyndigheten_api(path)[[1]][1:2]
        
        Parti...1                              `Röster 2022`
       <chr>                                          <dbl>
     1 Moderaterna                                  1187350
     2 Centerpartiet                                 417851
     3 Liberalerna (tidigare Folkpartiet)            286503
     4 Kristdemokraterna                             333327
     5 Arbetarepartiet-Socialdemokraterna           1897965
     6 Vänsterpartiet                                414604
     7 Miljöpartiet de gröna                         314579
     8 Sverigedemokraterna                          1282352
     9 Övriga anmälda partier                         92698
    10 Giltiga Röster                               6227229
    11 Ogiltiga röster - inte anmälda partier          3379
    12 Ogiltiga röster - blanka                       59218
    13 Ogiltiga röster - övriga                       31137
    14 Valdeltagande vallokaler                     6320963
    15 Röstberättigade                              7772120

 
    2)  get_p()[1:5,c(1,3)]
    
                              parties      shares 2022(%)
    1                        Moderaterna     0.19067068
    2                      Centerpartiet     0.06710063
    3 Liberalerna (tidigare Folkpartiet)     0.04600810
    4                  Kristdemokraterna     0.05352734
    5 Arbetarepartiet-Socialdemokraterna     0.30478484
    
    
    3) get_p_a()[2,c(1,3)]
    
          parties          parties shares 2022 including assembly districts(%)
    1   Moderaterna                                  0.19100886
    2 Centerpartiet                                  0.06722063
